ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-09 rebuttal.tex

\begin{response}
    %
    At present, this is not possible; only a single \verb|composition| block is allowed in the
    \verb|common-properties| section. However, we are considering modifying the behavior of the
    \verb|common-properties| section, and discussion is ongoing in
    \url{https://github.com/pr-omethe-us/PyKED/issues/67}.
    %
\end{response}

\begin{reviewer}
    %
    13.~Page 6, line 12 describes the initial efforts of building an open repository of ChemKED
    files, on GitHub. Is this the most efficient way for making a publically available database? One
    issue with this is the fact that adding files is done via pull requests, which have to be
    verified and approved by the owners of the repository. Therefore a certain delay is inevitable.
    %
\end{reviewer}

\begin{response}
    %
    We agree that submitting files to the ChemKED database on GitHub will inevitably incur some
    delay; however, we see the human intervention step as necessary and important. In much the same
    way that review of manuscripts provides a certain surety of the minimal quality of the article,
    we see review of data being added to the database as a minimal quality check; for instance, does
    the reference exist, has the data already been added to the database, are the files styled
    consistently, etc. Furthermore, such human review can help to catch some errors that may be
    introduced by manual creation of the files, as pointed out by the reviewer previously.

    Moreover, all existing databases have a similar requirement (whether explicitly stated or
    not), where users submit data files for inclusion that are approved by the database owners after
    some review. In this sense, we actually see the Pull Request mechanism of GitHub as an
    advantage, since all reviews can be done publicly and some of the review procedures (style
    checks, reference validity, etc.) may be done automatically by a script associated with the
    GitHub repository. In this way, the entire community can contribute to improving the quality of
    the database.

### 2017-10-09 pyked.tex
minor edits to paragraph about open

Finally, the closed and opaque natures of the PrIMe standard and associated Data Warehouse limit
contributions and community development of the PrIMe standard and compatible data files and tools.
In this sense, we mean ``closed'' as a contrast to open source, open science, and open data, as
defined by the Open Knowledge Institute~\cite{openknowledge} or the Open Source
Initiative~\cite{opensource}. Although most commonly applied to software, the distinction between
open and closed is becoming increasingly important in science and research. In brief, the Open
Knowledge Institute defines open knowledge as ``free to access, use, modify, and share... — subject,
at most, to measures that preserve provenance and openness''~\cite{openknowledge}, while the Open
Source Institute focuses on software and declares that a project must provide free and unrestricted
access to the source code, allow free redistribution, permit derived works, and not discriminate
against any people or areas of work, along with a few other criteria~\cite{opensource}.

>>>>

Finally, the closed and opaque natures of the PrIMe standard and associated Data Warehouse limit
contributions and community development of the PrIMe standard and compatible data files and tools.
In this sense, we mean ``closed'' as a contrast to open source, open science, and open data, as
defined by the Open Knowledge Institute~\cite{openknowledge} or the Open Source
Initiative~\cite{opensource}. Although most commonly applied to software, the distinction between
open and closed is becoming increasingly important in science and research. In brief, the Open
Knowledge Institute defines open knowledge as ``free to access, use, modify, and
share\textellipsis — subject, at most, to measures that preserve provenance and
openness''~\cite{openknowledge}, while the Open Source Institute focuses on software and declares
that a project must provide free and unrestricted access to the source code, allow free
redistribution, permit derived works, and not discriminate
against any people or areas of work, along with a few other criteria~\cite{opensource}.
